### 2018-03-26 Paper/intro.tex
...

Classical Molecular Dynamics (MD) is commonly used to study thermal transport in material systems 
especially in situations where transport due to phonon-phonon interactions is predominant. These 
systems typically comprise non-metallic elements such as carbon (nanotubes, fullerenes, graphite, etc.),
silicon and germanium.

>>>>

Classical Molecular Dynamics (MD) is commonly used to study thermal transport by means of phonons in material 
systems comprising non-metallic elements such as carbon, silicon, germanium.
